---
title: "BASS"
output: github_document
bibliography: README-bib.bib
---

[![License: GPL v3](https://img.shields.io/badge/License-GPLv3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)
`r badger::badge_devel("lanl/BASS", "purple")`
`r badger::badge_cran_release("BASS", "orange")`


 

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(BASS)
```



BASS is an R package for fitting Bayesian Adaptive Spline Surface models [available on CRAN](https://CRAN.R-project.org/package=BASS) with a development version [available on GitHub](https://github.com/lanl/BASS).  BASS models most closely resemble Bayesian multivariate adaptive regression splines (Bayesian MARS).

To install the development version, use

```{r, eval = F}
# install.packages("devtools")
devtools::install_github("lanl/BASS")
```

Examples of uses are in @francom2018sensitivity and @francom2019inferring and explicit code examples are given in the [R package vignette](https://CRAN.R-project.org/package=BASS/vignettes/).

# References
